\huge \systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-07-10 poster.tex
final poster

\author{Kevin Ellis, Lucas Morales, Mathias Sabl\'e Meyer, Maxwell Nye, Armando Solar-Lezama, Joshua B. Tenenbaum} % Author(s)

@@

\end{tikzpicture}
  \end{minipage}
\hspace{0.1cm}\begin{tabular}{ll}
    \toprule
    Example synthesized programs &Proposed $\lambda$-expression\\\midrule
    %% \begin{tabular}{l}
    %%   \code{($\lambda$ ($\ell$) (map ($\lambda$ (x) (index x $\ell$))}\\
    %%   \phantom{\code{($\lambda$ ($\ell$) (map }}\code{(range (- (length $\ell$) 1))))}\\
    %%   \code{($\lambda$ ($\ell$) (map ($\lambda$ (x) (index x $\ell$))}\\
    %%   \phantom{\code{($\lambda$ ($\ell$) (map }}\code{(range (+ 1 1))))}\\
    %% \end{tabular}&
    %% \begin{tabular}{l}
    %%   \code{(map ($\lambda$ (x) (index x $\ell$))}\\
    %%   \phantom{\code{(map)}}\code{(range $\alpha$))}\\
    %% \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{($\lambda$ (s) (map ($\lambda$ (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\\hspace{0.2cm}\code{   (if (= x $\alpha$) $\beta$ x))) s)}
      \end{tabular}
\\\bottomrule\\
\end{tabular}
\caption{\textbf{Left:} syntax trees of two programs sharing common structure,
highlighted in {\orange{orange}},
  from which we extract a fragment and add it to the DSL (bottom). \textbf{Right:} actual programs,
  from which we extract fragments that perform character substitutions.}\label{fragmentExample}
\end{figure}

@@

  \newcommand{\dreamSize}{5.5cm}
  \begin{tabular}{|lll|}\multicolumn{3}{c}{\textbf{12 (of 132) Tasks}}\\\hline
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_3_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_4_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow1_h.png}\\
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow2_random_1.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/hexa_vh.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/star_5_h.png}\\
        \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/star_vh.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/spiral6_h.png}&
        \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/star_7_h.png}\\

  \vspace{2cm} \emph{Left:}  Agent controls a `pen' -- tasked with drawing pictures. \\\emph{Right:} During Sleep-R,
  agent `dreams' by sampling programs from learned DSL and rendering them.

@@

\begin{block}{Learning from Scratch}
  Start w/ McCarthy 1959 Lisp: recursion, conditionals, lists.
  Train on 22 programming exercises.
  After 93 hours on 64 CPUs, rediscovers 9 functional programming staples: \code{map},
  \code{fold}, \code{zip}, \code{unfold}, \code{index}, \code{length}, \code{range}, \code{incr}, \code{decr}.

\begin{block}{Generative models of text}
    Learn probabilistic program: a stochastic regex\begin{figure}
\centering
%\tiny
\tabcolsep=2pt
\vspace{0pt}
\begin{tabular}{cc}
\begin{tabular}{ccc}
\multicolumn{3}{c}{Tasks:}\\
\hline
cut&F &Moss Side \\ 
control&CL &Burnage \\
control&F & City Centre\\
cut& PCFL& Brooklands \\
\multicolumn{3}{c}{Learned generative models:}\\
\hline
\scode{\textbackslash l*\textbackslash l} & \scode{((\textbackslash
u\textbackslash u)*)\textbar F}& \scode{( \textbar\textbackslash
u\textbackslash w*)*} \\
\multicolumn{3}{c}{Samples from synthesized generative models:}\\
\hline
ya&DQDF & Vr DR \\ 
glrwfdcnc&F &BeF lKQ \\
mgs&F& W\\
piljnl& KI& kqBfZ 0 \\
kj& F& ON\\
zci& GL& Bttc \\
sxpm& F& S \\
\hline
\\
\end{tabular} 
&
\begin{tabular}{c}
\begin{tabular}{l}
\multicolumn{1}{c}{Learned DSL:}\\
\hline
$f_1() = $ \scode{\textbackslash u\textbackslash w*}\\
$f_2(x) = $ \scode{($x$|$f_1$)*} $=$ \scode{($x$|\textbackslash
u\textbackslash w*)*}\\
$f_3(x) = f_2(\scode{space}) = $\scode{( \textbar\textbackslash
u\textbackslash w*)*}\\
\hline
$f_4(x) = $ \scode{($x$*$x$)}\\
\emph{ (equivalent to regex `plus')}\\
$f_5() = f_4(\scode{\textbackslash l}) = \scode{\textbackslash
l*\textbackslash l}$\\
\hline
\end{tabular}
\\
\\
\includegraphics[width=.4\linewidth]{figures/nampiregexjoshcurve3.eps} 
\end{tabular}
\end{tabular}
\vspace{-.3cm}
%\caption{regex stuff}
\end{figure}

>>>>

\author{Kevin Ellis, Lucas Morales, Mathias Sabl\'e Meyer, Maxwell Nye, Luke Hewitt,\\ Armando Solar-Lezama, Joshua B. Tenenbaum} % Author(s)

@@

\end{tikzpicture}
  \end{minipage}
\hspace{0.1cm}\begin{tabular}{ll}
    \toprule
    Example synthesized programs &Proposed $\lambda$-expression\\\midrule
    %% \begin{tabular}{l}
    %%   \code{($\lambda$ ($\ell$) (map ($\lambda$ (x) (index x $\ell$))}\\
    %%   \phantom{\code{($\lambda$ ($\ell$) (map }}\code{(range (- (length $\ell$) 1))))}\\
    %%   \code{($\lambda$ ($\ell$) (map ($\lambda$ (x) (index x $\ell$))}\\
    %%   \phantom{\code{($\lambda$ ($\ell$) (map }}\code{(range (+ 1 1))))}\\
    %% \end{tabular}&
    %% \begin{tabular}{l}
    %%   \code{(map ($\lambda$ (x) (index x $\ell$))}\\
    %%   \phantom{\code{(map)}}\code{(range $\alpha$))}\\
    %% \end{tabular}\\\midrule
    \begin{tabular}{l}
      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\
      \hspace{0.4cm}\code{ (if (= x '.') '-' x))) s)}\\
      \code{($\lambda$ (s) (map ($\lambda$ (x) }\\
      \hspace{0.4cm}\code{ (if (= x '-') ',' x))) s)}\\
      \end{tabular}&
    \begin{tabular}{l}      \code{($\lambda$ (s) (map ($\lambda$ (x)}\\\hspace{0.2cm}\code{   (if (= x $\alpha$) $\beta$ x))) s)}
      \end{tabular}
\\\bottomrule\\
\end{tabular}
\caption{\textbf{Left:} syntax trees of two programs sharing common structure,
highlighted in {\orange{orange}},
  from which we extract a fragment and add it to the DSL (bottom). \textbf{Right:} actual programs,
  from which we extract fragments that perform character substitutions.}\label{fragmentExample}
\end{figure}
\vspace{-1cm}
\end{block}

  \newcommand{\dreamSize}{5.5cm}
  \begin{tabular}{|lll|}\multicolumn{3}{c}{\textbf{12 (of 136) Tasks}}\\\hline
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_3_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/square/trimmed/train_square_4_h.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow1_h.png}\\
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/snow2_random_1.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/hexa_vh.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/star_5_h.png}\\
        \includegraphics[width = \dreamSize]{turtleTasks/six/trimmed/star_vh.png}&
    \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/spiral6_h.png}&
        \includegraphics[width = \dreamSize]{turtleTasks/logoTasks/trimmed/star_7_h.png}\\

  \vspace{2cm} \textbf{Left:}  Agent controls a `pen' -- tasked with drawing pictures. \textbf{Right:} During Sleep-R,
   `dream' by sampling programs from learned DSL and rendering them.

@@

@@

\begin{block}{Generative models of text}
  \begin{figure}
\centering
%\tiny
\tabcolsep=12pt
\begin{tabular}{ccc}\toprule 
\multicolumn{3}{c}{Three Tasks}\\
\hline
1.14531&F&110.9 \\ 
?&CL&163.2 \\
1.29857&F&207.3\\
?&PCFL&143.3 \\\\\midrule 
\multicolumn{3}{c}{Three learned generative models}\\
\hline
 \pop{\scode{?\textbar(1.\textbackslash d+)}}& \pop{\scode{((\textbackslash u\textbackslash u)*)\textbar F}}& \pop{\scode{\textbackslash d\textbackslash d\textbackslash d.\textbackslash d}} \\\\\midrule 
 \multicolumn{3}{c}{Samples from generative models}\\
\hline
1.61&DQDF& 343.8 \\ 
?&F&241.2\\
?&F&647.5\\
1.2&KI&246.8%% \\
%% 1.5080987&F&728.6\\
%% ?&GL&029.3\\
%% 1.453&F&289.1\\
%%     \hline
\\

\midrule \multicolumn{3}{c}{Learned DSL}\\\midrule
\multicolumn{3}{l}{\popp{\scode{$f_1 = $ \textbackslash u\textbackslash w*}}
\hspace{3cm}\popp{\scode{$f_2(x) = $($x$|$f_1$)*}}}\\% $=$ \scode{($x$|\textbackslash u\textbackslash w*)*}}\\
\multicolumn{3}{l}{\popp{\scode{$f_3 = f_2(\scode{`` ''}) = $( \textbar\textbackslash u\textbackslash w*)*}}}\\
\multicolumn{3}{l}{\hspace{1cm}\emph{($f_3$: whitespace delimited words)}}\\
\multicolumn{3}{l}{\popp{$f_4(x) = $ \scode{($x$*$x$)}}\hspace{1cm}\emph{($f_4$: regex `plus')}}
\end{tabular}
\vspace{-.3cm}
%\caption{regex stuff}
\end{figure}

\end{block}
\begin{block}{Learning from Scratch}
  Start w/ McCarthy 1959 Lisp: recursion, conditionals, lists.
  Train on 22 programming exercises.
  After 93 hours on 64 CPUs, rediscovers: \code{map},
  \code{fold}, \code{zip}, \code{unfold}, \code{index}, \code{length}, \code{range}, \code{incr}, \code{decr}.
